Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-15 paper/paper.tex
Fixing lem:1req

We define the algorithm \TAlg{} in the following way.
\TAlg{} maintains components for each node.
Intially, each node is in its own singleton component.
For each pair of nodes \TAlg{} maintains a counter, initiated $0$, and upon receiving a request to this pair while its nodes are located on different servers, it increases the counter by $1$.
If a counter for a pair $(u,v)$ reaches $\alpha$, \TAlg{} merges the components of $u$ and $v$, and moves to the closest partition, where it each component has all of its nodes in one server.
If no such partition exists, \TAlg{} resets all components to singletons and all counters to $0$.

@@

\begin{lemma}
  \label{lem:1req}
  A single repartition incurs the cost at most $3\cdot\alpha$ for \TAlg.
\end{lemma}

\begin{proof}
  If no partition of \TAlg's components exist, then it performs no repartition, and serves the request remotely, incurring the cost $1$.
  Hence, in the following we bound the cost of moving to component-respecting partition.

  We distinguish between three types of clusters: $C_1, C_2, C_3$,
  which we define as follows.
  A cluster of type $C_1$ the cluster contains $3$ singleton components (this is also the initial configuration of any cluster).
  A cluster of type $C_2$  contains one component of size $2$ and one component of size $1$.
  Finally, a cluster of type $C_3$  contains one component of size $3$.

    Consider a request $(u, v)$ and let $U, V$ be clusters of these nodes.
    If $U=V$, then the request does not require a reconfiguration and GREEDY incurs no cost.
    Otherwise, we consider cases upon the type of clusters $U$ and $V$.
    Note that this is impossible that either $U$ or $V$ is $C_3$ as otherwise we encounter a component of size $4$ and this would contradict the case assumption that the component-respecting partition exists.
    If either $U$ or $V$ is $C_1$, then either cluster can fit the merged component, and the rebalance is local within $U$ and $V$, for the cost of at most $3$ migrations.

    Finally, we consider the case where both $U$ and $V$ are $C_2$. Note that $(u,v)$ cannot both belong to a component of size $2$, as this would mean that \TAlg{} has the component of size $4$, a contradiction with the case assumption that the component-respecting partition exists. 
    If either $u$ or $v$ belongs to a component of size $2$ then it suffices to exchange components of size $1$ between $U$ and $V$.
    Finally, if $u$ and $v$ belong to components of size $1$, then we must place them in a cluster different from $U$ and $V$.
    Note that in such case, a $C_1$-type cluster $W$ exists, as otherwise the input graph would not have a perfect partition. In this case GREEDY exchanges the nodes $u$ and $v$ with any two nodes of $W$, for the total cost of $2\cdot \alpha$.
\end{proof}

>>>>

We define the algorithm \TAlg{} in the following way.
\TAlg{} maintains components for each node.
Intially, each node is in its own singleton component.
For each pair of nodes \TAlg{} maintains a counter, initiated $0$, and upon receiving a request to this pair while its nodes are located on different servers, it increases the counter by $1$.
If a counter for a pair $(u,v)$ reaches $\alpha$, \TAlg{} merges the components of $u$ and $v$, and moves to the closest partition, where it each component has all of its nodes in one server.
If no such partition exists, \TAlg{} resets all components to singletons and all counters to $0$ and ends the phase.

@@

\begin{lemma}
  \label{lem:1req}
  A single repartition performed by \TAlg{} incurs the cost at most $3\cdot\alpha$.
\end{lemma}

\begin{proof}
  If no partition of \TAlg's components exist, then it performs no repartition and the cost is $0$.
  Hence, in the following we bound the cost of moving to component-respecting partition.
  We define three types of clusters, $C_1, C_2, C_3$; in cluster of type $C_i$, the size of the largest component contained in this cluster is $i$.

  %We distinguish between three types of clusters: $C_1, C_2, C_3$,
  %which we define as follows.
  %A cluster of type $C_1$ the cluster contains $3$ singleton components (this is also the initial configuration of any cluster).
  %A cluster of type $C_2$  contains one component of size $2$ and one component of size $1$.
  %Finally, a cluster of type $C_3$  contains one component of size $3$.

    Consider a request $(u, v)$ and let $U, V$ be clusters of these nodes.
    If $U=V$, then the request does not require a reconfiguration and \TAlg{} incurs no cost.
    Otherwise, we consider cases upon the type of clusters $U$ and $V$.
    Note that this is impossible that either $U$ or $V$ is $C_3$ as otherwise we encounter a component of size $4$ and this would contradict the case assumption that the component-respecting partition exists.
    If either $U$ or $V$ is $C_1$, then this cluster can fit the merged component, and the rebalance is local within $U$ and $V$, for the cost of at most $3$ migrations.

    Finally, we consider the case where both $U$ and $V$ are $C_2$. Note that $(u,v)$ cannot both belong to a component of size $2$, as this would mean that \TAlg{} has the component of size $4$, a contradiction with the case assumption that the component-respecting partition exists. 
    If either $u$ or $v$ belongs to a component of size $2$, then it suffices to exchange components of size $1$ between $U$ and $V$.
    Finally, if $u$ and $v$ belong to components of size $1$, then we must place them in a cluster different from $U$ and $V$.
    Note that in such case, a $C_1$-type cluster $W$ exists, as otherwise no component-respecting partition exists. In this case \TAlg{} exchanges the nodes $u$ and $v$ with any two nodes of $W$, for the total cost of $2\cdot \alpha$.
\end{proof}
